\cvsection{Experience}

\begin{cventries}
  \cventry
    {Teaching Assistant} % Job title
    {Purdue University} % Organization
    {Fort Wayne, IN} % Location
    {Aug. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {CS590 - CyberSecurity}
		\item {CS232 - Intro to C and Unix}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {CGI Group Inc.} % Organization
    {Bengaluru, India} % Location
    {Aug. 2017 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { \textbf{DevOps} - A CGI internal project in which my role was automating the build and deployment process and also JUnit and SOAPUI scans of a certain application using dev-ops tools. This project was the first implementation of Dev-ops methodology at CGI.}
        \item { \textbf{Customer Assisted Collection System} - A CGI internal project in which my role was in fixing front end defects using HTML, CSS, JavaScript and JSP pages.}
        \item { \textbf{Xi, The Virtual Assistant} - A speech based chat bot which responds to pre-trained commands to perform certain functions.This application was developed using Angular 5, Java Spring boot Framework, MySQL and MongoDB. We have used Google Dialog Flow to train the bot.}
      \end{cvitems}
    }

  \cventry
    {DevOps Intern} % Job title
    {Coppernine SoftTech} % Organization
    {Hyderabad, India} % Location
    {May. 2016 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { \textbf{Openfoodnetwork India} - Open Food Network is an open-source web-infrastructure project which aims at decentralizing the food distribution system by enabling people and communities to build their own distribution initiatives and cooperate with each other. My role as a DevOps Intern in this project was in setup, deployment and compatibility test of the source code of openfoodnetwork which was prior launched in Australia.}
      \end{cvitems}
    }
\end{cventries}
